---
title: "Alcohol vs Seat choice"
author: "Genesis Alfaro"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The box for the back rows are much largerthan the front and middle seats. The red dots which are the outliers, are shown above each box. The differance in sizes will be ran with a series of t.test,s, two at a time to shows the significance.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The number of people who sat in the back row was 33. The front row contained 33 people, and the middle had the largest amount with 83.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The inferential tests shows that the probablity is too low, at 0.000116. We reject the null hypothesis as is.
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```
A multiple comparision test showcases a substantial difference or a lack of using each pair of data. The comparison of the middle row and the front row had little to no differance to eachother. This is shown by the 0 borken line, this bracket is placed where this broken line is and explains there is no difference in the data. The middle and back seats are on the right portion of the graph and show a negative result, based on the bottom line, placing it at approximately -11. The front and back portions were compared and showed the most significant change in numerical data. The bracket is in the negative numbers, at around -13. This inference explains the most drinking was done by the back row.

## Conclusions


